An Engineered Empirical Burnstein Bound

### 2018-08-21 paper/main.tex
update paper

Our first probability bound is a Chernoff bound on the sample mean. This bound is not new and was derived by Wassily Hoeffding \cite{hoeffding1} and has subsequently been a subject of discussion and many further developments \cite{hoeffding2,Bentkus08boundsfor,Pinelis2014,zbMATH00812598,MR1782937}.

>>>>

Our first probability bound is a Chernoff bound on the sample mean. This bound is not new and was derived by Wassily Hoeffding \cite{hoeffding1} and has subsequently been a subject of discussion and many further developments \cite{hoeffding2,Bentkus08boundsfor,Pinelis2014,zbMATH00812598}.
